Visualizations for article

### 2015-12-01 101-visualizations-for-article.Rmd
Refactor to use cached LSH objects

```{r}
cache_corpus <- "cache/corpus-sections-minash-n120-seed623.rda"
load(file = cache_corpus)
cache_lsh <- "cache/lsh-sections.rda"
load(file = cache_lsh)
borrowings <- section_scores %>% 
  rename(section_a = a, section_b = b, similarity = score) %>% 
  mutate(dissimilarity = 1 - similarity,
         code_a = extract_code_names(section_a),
         code_b = extract_code_names(section_b),
         year_a = extract_date(code_a),
         year_b = extract_date(code_b))
codes <- c(borrowings$code_a, borrowings$code_b) %>% unique()
```

@@

```{r}
CA1851 <- best_section_matches("CA1851", borrowings, threshold = 0.15)
CA1851
summarize_borrowings(CA1851)
```

@@

```{r}
section_pct <- codes %>% 
  mclapply(best_section_matches, scores = borrowings, threshold = 0.15)  %>% 
  mclapply(summarize_borrowings) %>% 
  bind_rows()
section_pct
```

>>>>

```{r}
load("cache/corpus-lsh.rda")
codes <- c(scores$code_a, scores$code_b) %>% unique()
```

@@

```{r}
CA1851 <- best_section_matches("CA1851", scores, threshold = 0.15)
CA1851
summarize_borrowings(CA1851)
```

@@

```{r}
section_pct <- codes %>% 
  mclapply(best_section_matches, scores = scores, threshold = 0.15)  %>% 
  mclapply(summarize_borrowings) %>% 
  bind_rows()
section_pct
```
